---
title: "data607_project1"
author: "Ritesh Lohiya"
date: "February 23, 2018"
output: html_document
---
```{r}
library(stringr)
```

Getting the Chess data:

```{r}
vars <- c("pair_num", "player_name", "total_points", "Round1", "Round2", "Round3", "Round4", "Round5", "Round6", "Round7", "LR")
data1 <- read.table("https://raw.githubusercontent.com/Riteshlohiya/Data607_Project1/master/tournamentinfo.txt", header = FALSE, skip = 4, sep = "|", fill = TRUE, stringsAsFactors = FALSE, col.names = vars)
head(data1)
```

Removing the hyphens and all the blank strings and also the Line return column(LR):

```{r}
data2 <- subset(data1, !player_name == "", select = c(pair_num:Round7))
head(data2)
```

Each player information is spread across 2 lines. Frirst we need to trim and remove the spaces:

```{r}
for (i in 1:length(data2)) {
  data2[, i] <- str_trim(data2[, i])
}
head(data2)
```

Now instead of 2 rows, arrange it in one row:

```{r}
for (i in 1:nrow(data2)) {
  data2$player_state[i] <- data2$pair_num[i + 1]
  data2$player_rating[i] <- str_trim(str_extract(data2$player_name[i + 1], "[[:blank:]]{1}[[:digit:]]{3,4}"))
}
data2 <- subset(data2, !is.na(player_rating))
head(data2)
```

The details for players playing against opponents:
```{r}
for (i in 4:10) {
  data2[, i] <- str_trim(str_extract(data2[, i], "[[:space:]]+[[:digit:]]{1,2}"))
}
head(data2)
```

Finding the oppenent ratings:

```{r}
for (i in 1:nrow(data2)) {
  for(j in 4:10) {
    data2[i,j] <- data2[data2$pair_num == data2[i,j],12][1]
    
  }
}

head(data2)
```

Finding average rating of opponents:

```{r}
for (i in 4:10) {
  data2[, i] <- as.numeric(data2[, i])
}
data2$player_rating <- as.numeric(data2$player_rating)
data2$total_points <- as.numeric(data2$total_points)
data2$avg_opponent_rating <- round(round(rowMeans(data2[, c(4:10)], na.rm = TRUE), 1))
head(data2)
```

Now writing only the required columns to the .csv file:

```{r}
final_data <- subset(data2, TRUE, c(player_name, player_state, total_points, player_rating, avg_opponent_rating))
row.names(final_data) <- 1:64
write.table(final_data, file = "C:/Users/Arnav/Documents/GitHub/Data607_Project1/tournament_data.csv", sep = ",", row.names = FALSE)
```





